---
title: "590R Final"
format: html
excute:
  error:true
  eval:true
---
install.packages("renv")
renv::init()
install.packages("gtsummary") 
install.packages("tidyverse")
renv::snapshot()

```{r}
library(gtsummary)
library(tidyverse)
chocolate <- read_csv(here::here("chocolate data", "chocolate.csv"))
```


```{r}
#| label: tbl-one
#| tbl-cap: "Chocolate Ratings Base on Bean's Country Origin"
table1 <- tbl_summary( 
  chocolate,
  by = rating,
  include = c(country_of_bean_origin),
  label = list(
    country_of_bean_origin ~ "Country of Bean Origin"),
  missing_text = "Missing")
table1
```
Venezuela's bean received the most number of level 4 ratings out of all countries, about (`r inline_text(table1, variable = "country_of_bean_origin", level = "Venezuela", column = "stat_12")`) times

@tbl-one is a table extracted from from Github's tidytuesday database 
```{r}
#| label: tbl-two
#| tbl-cap: "Regression on Cocoa Percent from Ratings and review date"
logistic_model <- glm(as.factor(chocolate$cocoa_percent) ~ rating + review_date,
									 data = chocolate, family = binomial())
tbl_regression(
	logistic_model,
	exponentiate = TRUE)
```

```{r}
#| label: fig-hist
#| fig-cap: "Total Chocolate Review Date"
hist(chocolate$review_date)
```
@fig-hist shows distribution of the review dates 
```{r}
#function
x <- c(chocolate$rating)
rating_mean<- function(x) {
  n <- length(x)
  mean_val <- sum(x) / n
  return(mean_val)}
rating_mean(x=x)

```

```{r}
stats <- list(n = nrow(chocolate),
              mean_rating = mean(chocolate$rating))
```

The average ratings from all of the `r stats$n` chocolates are `r stats$mean_rating`
